---
title: "Ivdrug"
author: "shaniqua"
date: "May 21, 2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avast <-filter(avast, Ivdrug == "user")
```
# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. 


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!--> The methods used for this was the chi-square and the fisher test. Were going to look at bar plots and compare them to see if they are different visually then look at the numerical results.

```{r}
results <-avast
trialtbl=xtabs(~infected+treatment,data=results)
```



```{r}
barchartGC(~infected+treatment,data=results, type ="percent")
```

## Numerical results


```{r}
colPerc(trialtbl)
rowPerc(trialtbl)
```

## inferential results

```{r}
chisqtestGC(trialtbl, graph = TRUE)
```

```{r}
fisher.test(trialtbl)
```

## CONCLUSION

Based on the results 60% of people got aids. The drugs aren't working. The Fisher test proves this statement, which says that it improves the chances that you get aids if you use the drug and your and Ivdrug user.

